Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
small typo fixes

To configure large networks, instead of considering individual
devices, operators classify devices into {\em roles}. A role refers to
specific functionality and is served by one or more devices. For instance, in a
data center, roles may be "top-of-rack," "aggregation," and "spine"
routers; and in a backbone network, they may be "core" and "border"
routers. While the network may have hundreds or thousands of devices---a scale
that is impossible for humans to handle---there tend to be a handful of roles.
%
Operators author a configuration {\em template} for each role. Templates are
macros that, given a network topology, can be instantiated with different concrete values to generate device configurations.

@@

All route announcements carry {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
%When BGP is used inside a datacenter, each router tends to be its own AS.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.

>>>>

To configure large networks, instead of considering individual
devices, operators classify devices into {\em roles}. A role refers to
specific functionality and is served by one or more devices. For instance, in a
data center, roles may be ``top-of-rack,'' ``aggregation,'' and ``spine''
routers; and in a backbone network, they may be ``core'' and ``border''
routers. While the network may have hundreds or thousands of devices---a scale
that is impossible for humans to handle---there tend to be a handful of roles.
%
Operators author a configuration {\em template} for each role. Templates are
macros that, given a network topology, can be instantiated with different concrete values to generate device configurations.

@@

All route announcements carry an {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
%When BGP is used inside a datacenter, each router tends to be its own AS.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.
